Weak gravitational lensing shear estimates with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey

### 2022-03-11 old/roman_metacal_v2.tex
rachel's comments v4.1

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} shear calibration framework using image simulations for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS). These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met. The weak lensing program of the \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%. To reach this goal, we can test our calibration process with these simulations and ultimately isolate the sources where these residual shear biases arise. In this work, we incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations and show first results for the reference HLIS using \textsc{metacalibration}. We find that compared with the non-calibrated results from previous work, \textsc{metacalibration} as used in current experiments can significantly reduce the shear calibration bias to the percent level. With the single-epoch images, across all three filters we are able to achieve a multiplicative bias $m=-1.34\%$ within 2 $\sigma$, while for coadd cutouts, $m=-2.33\%$ within about 4 $\sigma$. In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor. Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary. In the future, we will need to substantially increase the simulation volume by 400 (about the same size as the survey area of 2000 $deg^{2}$) to reach the precision necessary for the HLIS.
\end{abstract}

@@

Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime, observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS: \citealt{2013ExA....35...25D}) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}). As we observe more area of the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable. Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (\citealt{2011arXiv1110.3193L}), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply pre-existing shape measurement to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.

@@

In this study, we focus on the shear calibration bias, which describes the relationship between gravitational lensing shear $\gamma$ and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2013MNRAS.429..661M}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying and correcting these biases before the real survey begins is extremely important. \par

Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias. It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection. Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetection}; \citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} is that it can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.

One possible limitation might lie in the effect of undersampled images in space-based misssions like \emph{Euclid} and \emph{Roman}, which have such a small pixel scale that images will not be Nyquist sampled in the near-infrared (NIR) at the detector pixel scale (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem. We define the sampling factor of each filter in \emph{Roman} to be, 
\begin{equation}
    Q = \frac{\lambda_{min}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}). An image with sampling factor $Q < 2$ is not Nyquist sampled (i.e., undersampled). The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images. It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
Recently, \cite{2021MNRAS.502.4048K} (hereafter K21) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations. They found that for the \emph{Euclid} mission the shear estimate is biased by about 1$\%$. It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%. They show that these effects can be mitigated using additional weighting kernels in the measurement.

@@

This paper is organized as follows. We briefly discuss the simulation suite details we used and the updates we implemented for this project in Sec.~\ref{sec:sims}. Then, in Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}. We present the galaxy catalog properties and calibration results for single-band and multiband measurements in Sec.~\ref{sec:results}. Finally, in Sec.~\ref{sec:discussion}, we discuss how we will be able to constrain the shear bias better in terms of further updates in the image simulations and what we can conclude from this study.

\section{Simulations}
\label{sec:sims}
The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}. We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes. Then, the following properties are applied to each galaxy:
\begin{itemize}
    \item positions (RA, Dec),
    \item flux within each \emph{Roman} filter (F184/H158/J129/Y106),
    \item intrinsic galaxy shapes and random orientations,
    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots, and
    \item artificial gravitational lensing shears.
\end{itemize} 
Within four identical realizations of the simulation, we use four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}. This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute the multiplicative bias (\citealt{2019A&A...621A...2P}).

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{psf_rotation.pdf}
% 	\vspace*{-3mm}
    \caption{The rotation of the Roman PSF produced from the \texttt{galsim.roman} module. The position angle (PA) which determines the rotation of the focal plane is $0^{\circ}$ and $30^{\circ}$. The rotation of the PSF is particularly important when an object has multiple exposures. As more exposures are rotated relative to one another on the sky, the average impact of the PSF will be rounder. This will translate to a substantially less-elliptical coadd PSF.}
    \label{fig:psfrot}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{lowsnr_highsnr_galaxies.pdf}
	%\vspace*{-10mm}
    \caption{The top row shows the first entry of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for an object with low signal-to-noise ratio (S/N=9.69 in a single-epoch image). The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97 in a single-epoch image). The PSFs are shown in a log-scale.}
    \label{fig:singlecoadd}
\end{figure*}

\subsection{Updates to Simulation Capabilities}
In order to accomplish the science goals, and build and test weak lensing calibration pipelines for in \emph{Roman}, we have continued to update the realism of our image simulations. We have implemented and made updates to the following parts of the simulation framework to be able to better test shear calibration using \textsc{metacalibration}. 
\begin{itemize}
    \setlength\itemsep{1em}
    \item \textbf{Saturation Cuts}:
    We have implemented a pixel saturation limit of 100,000 electrons. This value is an approximate pixel saturation level, but in the next generation of the simulations we will use a more accurate pixel saturation limit measured directly from the flight candidate detectors.

@@

    \item \textbf{Single-band and Multiband Coadds}: 
    We have used the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps of individual objects. Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an image and mitigate the impacts of measurement noise, while allowing for better sampling of the image if the overlapping images are dithered. However, it is challenging to create a robust, continuous coadd PSF model over an entire image. This is mitigated if we instead construct small, local coadds (at the size of an object postage stamp cutout in this work), which is a method also utilized in \textsc{metadetection}. If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of approx. six in computing time, which is the average number of exposures from the reference survey. Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd can be better sampled due to dithering. For these reasons, we explore utilizing a coadding scheme for the \emph{Roman} galaxies. The detailed overview of the coadd process in \texttt{psc} is described in in Sec. \ref{subsec:psc}.

    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented the \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and was used to produce the weak lensing shape catalog in the DES Y3 analysis (\citealt{2020arXiv201103408G}). The \textsc{metacalibration} process can be performed on single-epoch or coadd images in each bandpass. With this calibration method, we hope to significantly reduce some of the shear calibration bias T21 measured in order to make comparisons of effects contributing to the bias more realistic and meaningful as we explore future \emph{Roman} pipeline development. The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}. 
    %\item (Any other changes?)
\end{itemize}

\subsection{Validations with Simple Simulations}
\label{subsec:simplesim}
The purpose of the simple simulations is to verify that there are no systematic biases at the fundamental levels of the simulation (e.g., no complex detector effects). These simple simulations play roles in ruling out the sources of systematic biases that may potentially be a problem in the use of \textsc{metacalibration} with space-based images.

The parameter choices are listed in Table. \ref{tab:params}. With these parameters set, we simulated images with varying galaxy model profile, PSF model profile, the artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition. We first verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough for the \emph{Roman} requirement (Fig. \ref{fig:metacal_shear_linear}). We then test the pipeline by doubling the background noise. Due to the \emph{Roman} being in NIR range, the expected background noise level in the images is higher compared to optical imaging surveys like DES. With this test, we can confirm that the treatment of correlated noise induced in \textsc{metacalibration} process for low S/N objects does not trigger any bias at the level we should be concerned (\citealt{2017ApJ...841...24S}). Another test with \emph{Roman} PSF instead of Gaussian PSF does guarantee that the PSF features particular to \emph{Roman} do not bias the shape recovery even though it is undersampled. Upon validating there does not exist any bias at the fundamental level, we began constructing coadd and more complex measurement pipeline. 
\begin{table}
    \centering
    \begin{tabular}[width=\columnwidth]{|p{3cm}||p{3cm}|p{3cm}|p{3cm}|}
    \hline
    Parameter & Value \\
    \hline
    Pixel scale & 0.11 arcsec/pixel\\
    Dither, SCA & 22535, 1 \\ 
    Bandpass & H158 \\
    Half-light radius & 1.0 arcsec\\
    Magnitude & randomly chosen from \emph{CANDELS} \\ 
    Stamp size & 32 pixels each side\\
    \hline
    \end{tabular}
    \caption{List of the parameter choices for the simple simulations.}
    \label{tab:params}
\end{table}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
    %\vspace*{-5mm}
    \caption{At first order, the \textsc{metacalibration} method only works for small shears. The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear. A larger input shear increases the signal-to-noise of bias estimates, but to keep this effect small compared to requirements, we limit input shears to $\pm 0.01$.}
    \label{fig:metacal_shear_linear}
\end{figure}

\section{Coadd and shear calibration pipelines}
\label{sec:methods}
Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman}. In order to do so, we need to build measurement pipelines within the current simulation framework that produces a final calibrated shear measurement. In this section, we present in detail how coadd images are produced with \texttt{psc} from the undersampled single-epoch images and how \textsc{metacalibration} is implemented to calibrates the measured shear using the \textsc{metacalibration} catalog.

\subsection{Postage Stamp Coadds}
\label{subsec:psc}
Coaddition is the process of summing information from multiple overlapping images. If the single-epoch images are dithered, a Nyquist-sampled image can be constructed out of multiple exposures of an object. While this process can also be beneficial in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images taken with telescopes that can rotate. When rotation is introduced, this coadding process becomes more complex to interpolate the image to stack a pixel grid. While coaddition can introduce new challenges and potential biases due to the complexity of coadding the original PSF and its interpolation scheme, the bias due to the undersampling of the original images can be mitigated by appropriately coadding dithered images.

@@

In practice, we compute the shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.

>>>>

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} shear calibration framework using image simulations for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS). These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met. The weak lensing program of the \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%. To reach this goal, we can test our calibration process with these simulations and ultimately isolate the sources where these residual shear biases arise. In this work, we incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations and show first results for the reference HLIS using \textsc{metacalibration}. We find that \textsc{metacalibration} as used in current experiments can significantly reduce the shear calibration bias to the percent level. With the single-epoch images, across all three filters we are able to achieve a multiplicative bias $m=(-1.34\pm 0.67)$\%, while for coadd cutouts, $m=(-2.33\pm 0.64)$\%. In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor. Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary. In the future, we will need to substantially increase the simulation volume by 400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary for the HLIS.
\end{abstract}

@@

Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime, observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS: \citealt{2013ExA....35...25D}) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}). As we observe more area of the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable. Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (\citealt{2011arXiv1110.3193L}), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and the \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply pre-existing shape measurement to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.

@@

Conventionally, these observational systematic biases are realized through a number of simulations and validations, and these propagate into the final galaxy shapes we measure. We quantify this impact as shear calibration bias. There have been several shear calibration and bias mitigation efforts that were proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias. It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection. Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetection}; \citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} is that it can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.

One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at its diffraction-limit (\citealt{2013PASP..125.1496S}). The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images. It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
Recently, \cite{2021MNRAS.502.4048K} (hereafter K21) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations. They found that for the \emph{Euclid} mission the shear estimate with \textsc{metacalibration} is biased by about 1$\%$. It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%. They show that these effects can be mitigated using additional weighting kernels in the measurement.

@@

This paper is organized as follows. We first introduce the formalism of shear bias and image sampling relevant to the space-based surveys in Sec.~\ref{sec:background}. We then briefly discuss the simulation suite details we used and the updates we implemented for this project in Sec.~\ref{sec:sims}. In Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}. We present the galaxy catalog properties and calibration results for single-band and multiband measurements in Sec.~\ref{sec:results}. Finally, in Sec.~\ref{sec:discussion}, we discuss how we will be able to constrain the shear bias better in terms of further updates in the image simulations and what we can conclude from this study.

\section{Background}
\label{sec:background}
In this section, we provide an overview of shear calibration bias within the weak lensing formalism and the brief introduction of image sampling defined through the Nyquist-Shannon Sampling Theorem.

\subsection{Shear Calibration Bias}
weak lensing quantities. shear, reduced shear, ellipticity, shear bias.
In this study, we focus on the shear calibration bias, which describes the relationship between gravitational lensing shear $\gamma$ and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2013MNRAS.429..661M}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying and correcting these biases before the real survey begins is extremely important. \par

\subsection{Image Sampling}
Based on the Nyquist-Shannon Sampling Theorem, 
we define the sampling factor of each filter in \emph{Roman} to be, 
\begin{equation}
    Q = \frac{\lambda_{min}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}). An image with sampling factor $Q < 2$ is not Nyquist sampled (i.e., undersampled).

\section{Simulations}
\label{sec:sims}
The base of our image simulations for the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}. We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes. Then, the following properties are applied to each galaxy:
\begin{itemize}
    \item positions (RA, Dec),
    \item flux within each \emph{Roman} filter (F184/H158/J129/Y106),
    \item intrinsic galaxy shapes and random orientations,
    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots, and
    \item artificial gravitational lensing shears.
\end{itemize} 
Within four identical realizations of the simulation, we use four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}. This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute the multiplicative bias (\citealt{2019A&A...621A...2P}).

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{psf_rotation.pdf}
% 	\vspace*{-3mm}
    \caption{The rotation of the Roman PSF produced by the \texttt{galsim.roman} module. The position angle (PA) which determines the rotation of the focal plane is $0^{\circ}$ and $30^{\circ}$ clockwise. These are drawn for SCA=1 and H158 bandpass at a native pixel scale. The rotation of the PSF is particularly important when an object has multiple exposures. As more exposures are rotated relative to one another on the sky, the average impact of the PSF will be rounder. This will translate to a substantially less-elliptical coadd PSF.}
    \label{fig:psfrot}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{lowsnr_highsnr_galaxies.pdf}
	%\vspace*{-10mm}
    \caption{The top row shows the first observation of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for a galaxy with low signal-to-noise ratio (S/N=9.69 in a single-epoch image). The bottom row shows the same for a galaxy with high signal-to-noise ratio (S/N=1552.97 in a single-epoch image). The PSFs are shown in a log-scale. The single epoch PSFs are almost identical, since there is no visually different feature for modeling them in different dithers and SCAs. Coadded PSFs look slightly different due to different numbers of single exposures. }
    \label{fig:singlecoadd}
\end{figure*}

\subsection{Updates to Simulation Capabilities}
In order to accomplish the science goals, and build and test weak lensing calibration pipelines for \emph{Roman}, we have continued to update the realism of our image simulations. We have implemented and made updates to the following parts of the simulation framework to be able to better test shear calibration using \textsc{metacalibration}. 
\begin{itemize}
    \setlength\itemsep{1em}
    \item \textbf{Saturation Cuts}:
    We have implemented a pixel saturation limit of 100,000 electrons. This value is an approximate pixel saturation level, but in the next generation of the simulations we will use a more accurate pixel saturation limit measured directly from the flight candidate detectors.

@@

    \item \textbf{Single-band and Multiband Coadds}: 
    We have used the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps of individual objects. Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an image and mitigate the impacts of measurement noise, while allowing for better sampling of the image if the overlapping images are dithered. However, it is challenging to create a robust, continuous coadd PSF model over an entire image. This is mitigated if we instead construct small, local coadds (at the size of an object postage stamp cutout in this work), which is a method also utilized in \textsc{metadetection}. If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of approx. six in computing time, which is the average number of exposures from the reference survey. Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd can be better sampled due to dithering. For these reasons, we explore utilizing a coadding scheme for the \emph{Roman} galaxies. The detailed overview of the coadd process in \texttt{psc} is described in Sec. \ref{subsec:psc}.

    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented the \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and was used to produce the weak lensing shape catalog in the DES Y3 analysis (\citealt{2020arXiv201103408G}). The \textsc{metacalibration} process can be performed on single-epoch or coadd images in each bandpass. With this calibration method, we hope to significantly reduce some of the shear calibration bias T21 measured in order to make comparisons of effects contributing to the bias more realistic and meaningful as we explore future \emph{Roman} pipeline development. The detailed overview of \textsc{metacalibration} can be found in Sec.~\ref{subsec:mcal}. 
    %\item (Any other changes?)
\end{itemize}

\subsection{Validations with Simple Simulations}
\label{subsec:simplesim}
The purpose of the simple simulations is to verify that there are no systematic biases at the fundamental levels of the simulation (e.g., no complex detector effects). These simple simulations play a role in ruling out the sources of systematic biases that may potentially be a problem in the use of \textsc{metacalibration} with space-based images.

The fixed parameters for the simulations are listed in Table. \ref{tab:params}. With these parameters, we simulated images with varying galaxy model profile, PSF model profile, the artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition. We set the basic light profiles for galaxies and PSF to be Gaussian. We first verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough for the \emph{Roman} requirement (Fig. \ref{fig:metacal_shear_linear}). We then test the pipeline by doubling the background noise. Due to \emph{Roman} being in NIR range, the expected background noise level in the images is higher compared to optical imaging surveys like DES. With this test, we can confirm that the treatment of correlated noise induced in the  \textsc{metacalibration} process for low S/N objects does not trigger any bias at the level we should be concerned (\citealt{2017ApJ...841...24S}). Another test with \emph{Roman} PSF instead of Gaussian PSF does guarantee that the PSF features particular to \emph{Roman} do not bias the shape recovery even though it is undersampled. Upon validating there does not exist any bias at the fundamental level, we began constructing coadd and more complex measurement pipeline. 
\begin{table}
    \centering
    \begin{tabular}[width=\columnwidth]{|p{3cm}||p{3cm}|p{3cm}|p{3cm}|}
    \hline
    Parameter & Value \\
    \hline
    Pixel scale & 0.11 arcsec/pixel\\
    Dither, SCA & 22535, 1 \\ 
    Bandpass & H158 \\
    Half-light radius & 1.0 arcsec\\
    Magnitude & randomly chosen from \emph{CANDELS} \\ 
    Stamp size & 32 pixels each side\\
    \hline
    \end{tabular}
    \caption{List of the parameter choices for the simple simulations.}
    \label{tab:params}
\end{table}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
    %\vspace*{-5mm}
    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our simulations. At first order, the \textsc{metacalibration} method only works for small shears. The next order effect is seen as a quadratic dependence of the multiplicative shear bias on the applied shear. A larger input shear increases the signal-to-noise of bias estimates, but to keep the non-linear effect small compared to requirements, we limit input shears to $\pm 0.01$.}
    \label{fig:metacal_shear_linear}
\end{figure}

\section{Coadd and shear calibration pipelines}
\label{sec:methods}
Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman} and to understand the factors that might contribute to any non-negligible bias. In order to do so, we need to build a measurement pipeline within the current simulation framework that produces a final calibrated shear measurement. In this section, we present in detail how coadd images are produced with \texttt{psc} from the undersampled single-epoch images and how \textsc{metacalibration} is implemented to calibrate the measured shear using the \textsc{metacalibration} catalog.

\subsection{Postage Stamp Coadds}
\label{subsec:psc}
Coaddition is the process of summing information from multiple overlapping images. If the single-epoch images are dithered, a Nyquist-sampled image can be constructed out of multiple exposures of an object. While this process can also be beneficial in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images taken with telescopes that can rotate. When rotation is introduced, this coadding process becomes more complex to interpolate the image to stack a pixel grid. While coaddition can introduce new challenges and potential biases due to the complexity of coadding the original PSF and its interpolation scheme, the bias due to the undersampling of the original images can be mitigated by appropriately coadding dithered images. (choice of psc? -> to avoid thinking about rotations of the whole image, coadding cutouts is much easier. )

@@

In practice, we compute the mean shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
